Article Title

### 2023-08-14 Markdown/Manuscript/Parent_PDF/Test.tex
updated intro

%% Per the spinger doc, new theorem styles can be included using built in style, 
%% but it seems the don't work so commented below
%\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

%% \theoremstyle{thmstyletwo}%
\theoremstyle{remark}
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

%% \theoremstyle{thmstylethree}%
\theoremstyle{definition}
\newtheorem{definition}{Definition}%

@@

\hypertarget{sec1}{%
\section{Introduction}\label{sec1}}

The Introduction section, of referenced text \citet{bib1} expands on the
background of the work (some overlap with the Abstract is acceptable).
The introduction should not include subheadings.

Springer Nature does not impose a strict layout as standard however
authors are advised to check the individual requirements for the journal
they are planning to submit to as there may be journal-level
preferences. When preparing your text please also be aware that some
stylistic choices are not supported in full text XML (publication
version), including coloured font. These will not be replicated in the
typeset article if it is accepted.

\hypertarget{sec2}{%
\section{Results}\label{sec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec3}{%
\section{This is an example for first level head---section
head}\label{sec3}}

\hypertarget{subsec2}{%
\subsection{This is an example for second level head---subsection
head}\label{subsec2}}

\hypertarget{subsubsec2}{%
\subsubsection{This is an example for third level head---subsubsection
head}\label{subsubsec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text.

\hypertarget{sec4}{%
\section{Equations}\label{sec4}}

Equations in \LaTeX~can either be inline or on-a-line by itself
(``display equations''). For inline equations use the \texttt{\$...\$}
commands. E.g.: The equation \(H\psi = E \psi\) is written via the
command \texttt{\$H\ \textbackslash{}psi\ =\ E\ \textbackslash{}psi\$}.

For display equations (with auto generated equation numbers) one can use
the equation or align environments:

\begin{equation}
\|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
\end{equation}

where, \begin{align}
D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
\end{align}

Notice the use of \texttt{\textbackslash{}nonumber} in the align
environment at the end of each line, except the last, so as not to
produce equation numbers on lines where no equation numbers are
required. The \texttt{\textbackslash{}label\{\}} command should only be
used at the last line of an align environment where
\texttt{\textbackslash{}nonumber} is not used.

\begin{equation}
Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
    \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
    + \frac{\ln(c_2/5)}{15} \right]
\end{equation}

The class file also supports the use of
\texttt{\textbackslash{}mathbb\{\}},
\texttt{\textbackslash{}mathscr\{\}} and
\texttt{\textbackslash{}mathcal\{\}} commands. As such
\texttt{\textbackslash{}mathbb\{R\}},
\texttt{\textbackslash{}mathscr\{R\}} and
\texttt{\textbackslash{}mathcal\{R\}} produces \(\mathbb{R}\),
\(\mathscr{R}\) and \(\mathcal{R}\) respectively (refer
Subsubsection~\ref{subsubsec2}).

\hypertarget{sec5}{%
\section{Tables}\label{sec5}}

Tables can be inserted via the normal \texttt{knitr::kable()} function
or other table-generating packages.

\begin{table}

\caption{\label{tab:tab1}Caption text}
\centering
\begin{tabular}[t]{r|r}
\hline
temperature & pressure\\
\hline
0 & 0.0002\\
\hline
20 & 0.0012\\
\hline
40 & 0.0060\\
\hline
60 & 0.0300\\
\hline
80 & 0.0900\\
\hline
100 & 0.2700\\
\hline
\end{tabular}
\end{table}

Tables can also be inserted via the normal table and tabular
environment. To put footnotes inside tables you should use
\texttt{\textbackslash{}footnotetext{[}{]}\{...\}} tag. The footnote
appears just below the table itself (refer
Tables\textasciitilde{}\ref{tab1} and \ref{tab2}). For the corresponding
footnotemark use \texttt{\textbackslash{}footnotemark{[}...{]}}

\begin{table}[h]
\caption{Caption text}\label{tab1}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2  & Column 3 & Column 4\\
\midrule
row 1    & data 1   & data 2  & data 3  \\
row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
\end{table}

\noindent The input format for the above table is as follows:

\begin{verbatim}
\begin{table}[<placement-specifier>]
\caption{<table-caption>}\label{<table-label>}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2 & Column 3 & Column 4\\
\midrule
row 1 & data 1 & data 2  & data 3 \\
row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
row 3 & data 7 & data 8  & data 9\footnotemark[2]\\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote.
This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.
This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote.
This is an example of table footnote.}
\end{table}
\end{verbatim}

\begin{table}[h]
\caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
\begin{tabular*}{\textwidth}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.}
\footnotetext[2]{Example for a second table footnote.}
\end{table}

\vfill\eject

In case of double column layout, tables which do not fit in single
column width should be set to full text width. For this, you need to use
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} instead of
\texttt{\textbackslash{}begin\{table\}} \texttt{...}
\texttt{\textbackslash{}end\{table\}} environment. Lengthy tables which
do not fit in textwidth should be set as rotated table. For this, you
need to use \texttt{\textbackslash{}begin\{sidewaystable\}} \texttt{...}
\texttt{\textbackslash{}end\{sidewaystable\}} instead of
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} environment. This environment
puts tables rotated to single column width. For tables rotated to double
column width, use \texttt{\textbackslash{}begin\{sidewaystable*\}}
\texttt{...} \texttt{\textbackslash{}end\{sidewaystable*\}}.

\begin{sidewaystable}
\caption{Tables which are too long to fit, should be written using the "sidewaystable" environment as shown here}\label{tab3}
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Projectile & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{This is an example of table footnote.}
\end{sidewaystable}

\hypertarget{sec6}{%
\section{Figures}\label{sec6}}

As per the \LaTeX~standards you need to use eps images for
\LaTeX~compilation and \texttt{pdf/jpg/png} images for \texttt{PDFLaTeX}
compilation. Use the \texttt{dev} knitr option to use the approrpate
format. This is one of the major difference between \LaTeX~and
\texttt{PDFLaTeX}. Each image should be from a single input .eps/vector
image file. Avoid using subfigures. The command for inserting images for
\LaTeX~and \texttt{PDFLaTeX} can be generalized. The package used to
insert images in \texttt{LaTeX/PDFLaTeX} is the graphicx package.
Figures can be inserted via the normal figure environment as shown in
the below example:

\begin{figure}
\includegraphics{Example_files/figure-latex/fig1-1} \caption{This is an example of a caption}\label{fig:fig1}
\end{figure}

\hypertarget{sec7}{%
\section{Algorithms, Program codes and Listings}\label{sec7}}

Packages \texttt{algorithm}, \texttt{algorithmicx} and
\texttt{algpseudocode} are used for setting algorithms in \LaTeX~using
the format:

\begin{verbatim}
\begin{algorithm}
\caption{<alg-caption>}\label{<alg-label>}
\begin{algorithmic}[1]
. . .
\end{algorithmic}
\end{algorithm}
\end{verbatim}

You may refer above listed package documentations for more details
before setting \texttt{algorithm} environment. For program codes, the
``program'' package is required and the command to be used is
\texttt{\textbackslash{}begin\{program\}} \texttt{...}
\texttt{\textbackslash{}end\{program\}}. A fast exponentiation
procedure:

Similarly, for \texttt{listings}, use the \texttt{listings} package.
\texttt{\textbackslash{}begin\{lstlisting\}} \texttt{...}
\texttt{\textbackslash{}end\{lstlisting\}} is used to set environments
similar to \texttt{verbatim} environment. Refer to the
\texttt{lstlisting} package documentation for more details.

A fast exponentiation procedure:

\lstset{texcl=true,basicstyle=\small\sf,commentstyle=\small\rm,mathescape=true,escapeinside={(*}{*)}}
\begin{lstlisting}
begin
  for $i:=1$ to $10$ step $1$ do
      expt($2,i$);  
      newline() od                (*\textrm{Comments will be set flush to the right margin}*)
where
proc expt($x,n$) $\equiv$
  $z:=1$;
  do if $n=0$ then exit fi;
     do if odd($n$) then exit fi;                 
        comment: (*\textrm{This is a comment statement;}*)
        $n:=n/2$; $x:=x*x$ od;
     { $n>0$ };
     $n:=n-1$; $z:=z*x$ od;
  print($z$). 
end
\end{lstlisting}

\begin{algorithm}
\caption{Calculate $y = x^n$}\label{algo1}
\begin{algorithmic}[1]
\Require $n \geq 0 \vee x \neq 0$
\Ensure $y = x^n$ 
\State $y \Leftarrow 1$
\If{$n < 0$}\label{algln2}
        \State $X \Leftarrow 1 / x$
        \State $N \Leftarrow -n$
\Else
        \State $X \Leftarrow x$
        \State $N \Leftarrow n$
\EndIf
\While{$N \neq 0$}
        \If{$N$ is even}
            \State $X \Leftarrow X \times X$
            \State $N \Leftarrow N / 2$
        \Else[$N$ is odd]
            \State $y \Leftarrow y \times X$
            \State $N \Leftarrow N - 1$
        \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{minipage}{\hsize}

\lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}

\begin{lstlisting}
for i:=maxint to 0 do begin \{ do nothing \} end; Write(`Case
insensitive'); Write(`Pascal keywords.');

\end{lstlisting}

\end{minipage}

\hypertarget{sec8}{%
\section{Cross referencing}\label{sec8}}

Figures and tables are labeled with a prefix (fig or tab, respectively)
plus the chunk label. Other environments such as equation and align can
be labelled via the \texttt{\textbackslash{}label\{\#label\}} command
inside or just below the \texttt{\textbackslash{}caption\{\}} command.
You can then use the label for cross-reference. As an example, consider
the chunk label declared for Figure~\ref{fig:fig1} which is fig1. To
cross-reference it, use the command
\texttt{Figure\ \textbackslash{}ref\{fig:fig1\}}, for which it comes up
as ``Figure~\ref{fig:fig1}''.

To reference line numbers in an algorithm, consider the label declared
for the line number 2 of Algorithm~\ref{algo1} is
\texttt{\textbackslash{}label\{algln2\}}. To cross-reference it, use the
command \texttt{\textbackslash{}ref\{algln2\}} for which it comes up as
line~\ref{algln2} of Algorithm~\ref{algo1}.

\hypertarget{subsec7}{%
\subsection{Details on reference citations}\label{subsec7}}

For citations of references, use~\citet{bib1} or \citep{bib2}.

\hypertarget{sec10}{%
\section{Examples for theorem like environments}\label{sec10}}

The documentclass for springer \texttt{sn-jnl.cls} contains 3 styling
that you can use to set new default for theorems and proofs type

\begin{description}
\item[\texttt{thmstyleone}]
Numbered, theorem head in bold font and theorem text in italic style
\item[\texttt{thmstyletwo}]
Numbered, theorem head in roman font and theorem text in italic style
\item[\texttt{thmstylethree}]
Numbered, theorem head in bold font and theorem text in roman style
\end{description}

For mathematics journals, theorem styles can be included as shown in the
following examples.

\begin{theorem}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

To add labels and subheadings, use LaTeX notation

\begin{theorem}[Theorem subhead]\label{thm1}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

Other environments are proposition, example, remark, definition, proof
and quote

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{proposition}
Example proposition text. Example proposition text. Example proposition
text. Example proposition text. Example proposition text. Example
proposition text. Example proposition text. Example proposition text.
Example proposition text. Example proposition text.

\end{proposition}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{example}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{example}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{remark}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{remark}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{definition}[Definition sub head]
Example definition text. Example definition text. Example definition
text. Example definition text. Example definition text. Example
definition text. Example definition text. Example definition text.

\end{definition}

Additionally a predefined ``proof'' environment is available. This
prints a ``Proof'' head in italic font style and the ``body text'' in
roman font style with an open square at the end of each proof
environment.

\begin{proof}
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text.

\end{proof}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec11}{%
\section{Methods}\label{sec11}}

Topical subheadings are allowed. Authors must ensure that their Methods
section includes adequate experimental and characterization data
necessary for others in the field to reproduce their work. Authors are
encouraged to include RIIDs where appropriate.

\textbf{Ethical approval declarations} (only required where applicable)
Any article reporting experiment/s carried out on
(i)\textasciitilde live vertebrate (or higher invertebrates),
(ii)\textasciitilde humans or (iii)\textasciitilde human samples must
include an unambiguous statement within the methods section that meets
the following requirements:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Approval: a statement which confirms that all experimental protocols
  were approved by a named institutional and/or licensing committee.
  Please identify the approving body in the methods section
\item
  Accordance: a statement explicitly saying that the methods were
  carried out in accordance with the relevant guidelines and regulations
\item
  Informed consent (for experiments involving humans or human tissue
  samples): include a statement confirming that informed consent was
  obtained from all participants and/or their legal guardian/s
\end{enumerate}

If your manuscript includes potentially identifying patient/participant
information, or if it describes human transplantation research, or if it
reports results of a clinical trial then additional information will be
required. Please visit
(\url{https://www.nature.com/nature-research/editorial-policies}) for
Nature Portfolio journals,
(\url{https://www.springer.com/gp/authors-editors/journal-author/journal-author-helpdesk/publishing-ethics/14214})
for Springer Nature journals, or
(\url{https://www.biomedcentral.com/getpublished/editorial-policies/\#ethics+and+consent})
for BMC.

\hypertarget{sec12}{%
\section{Discussion}\label{sec12}}

Discussions should be brief and focused. In some disciplines use of
Discussion or `Conclusion' is interchangeable. It is not mandatory to
use both. Some journals prefer a section `Results and Discussion'
followed by a section `Conclusion'. Please refer to Journal-level
guidance for any specific requirements.

\hypertarget{sec13}{%
\section{Conclusion}\label{sec13}}

Conclusions may be used to restate your hypothesis or research question,
restate your major findings, explain the relevance and the added value
of your work, highlight any limitations of your study, describe future
directions for research and recommendations.

In some disciplines use of Discussion or `Conclusion' is
interchangeable. It is not mandatory to use both. Please refer to
Journal-level guidance for any specific requirements.

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so
here.

Authors reporting data from electrophoretic gels and blots should supply
the full unprocessed scans for key as part of their Supplementary
information. This may be requested by the editorial team/s if it is
missing.

Please refer to Journal-level guidance for any specific requirements.

\bmhead{Acknowledgments}

Acknowledgments are not compulsory. Where included they should be brief.
Grant or contribution numbers may be acknowledged.

Please refer to Journal-level guidance for any specific requirements.

\hypertarget{declarations}{%
\section*{Declarations}\label{declarations}}
\addcontentsline{toc}{section}{Declarations}

Some journals require declarations to be submitted in a standardised
format. Please check the Instructions for Authors of the journal to
which you are submitting to see if you need to complete this section. If
yes, your manuscript must contain the following sections under the
heading `Declarations':

\begin{itemize}
\tightlist
\item
  Funding
\item
  Conflict of interest/Competing interests (check journal-specific
  guidelines for which heading to use)
\item
  Ethics approval
\item
  Consent to participate
\item
  Consent for publication
\item
  Availability of data and materials
\item
  Code availability
\item
  Authors' contributions
\end{itemize}

\noindent If any of the sections are not relevant to your manuscript,
please include the heading and write `Not applicable' for that section.

\begin{flushleft}
Editorial Policies for:

\noindent Springer journals and proceedings:
\url{https://www.springer.com/gp/editorial-policies}

\noindent Nature Portfolio journals:
\url{https://www.nature.com/nature-research/editorial-policies}

\noindent \textit{Scientific Reports}:
\url{https://www.nature.com/srep/journal-policies/editorial-policies}

\noindent BMC journals:
\url{https://www.biomedcentral.com/getpublished/editorial-policies}

\end{flushleft}

\begin{appendices}

\hypertarget{secA1}{%
\section{Section title of first appendix}\label{secA1}}

An appendix contains supplementary information that is not an essential
part of the text itself but which may be helpful in providing a more
comprehensive understanding of the research problem or it is information
that is too cumbersome to be included in the body of the paper.

For submissions to Nature Portfolio Journals please use the heading
``Extended Data''.

\end{appendices}

\bibliography{bibliography.bib}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage[normalem]{ulem}
\usepackage{threeparttablex}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

TEST

\bibliography{../Data/references.bib}
